Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-06-30 method.tex
No need to reintroduce the abbreviation 'S6/VSR3' in section 3
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1234 ccdd05d5-56c1-461a-bf98-85f6876523b4

In this section we describe a decomposition of the \CBC{} signal space that
reduces \TD\ filtering cost sufficiently to allow for the
possibility of \earlywarning\ detection with modest computing requirements.  We
expand on the ideas of \citet{Marion2004} and \citet{Buskulic2010} that describe a
multi-band decomposition of the compact binary signal space that resulted in
a search with minutes latency in \LIGO{}'s S6 and Virgo's VSR3 joint science
runs~\citep{HugheyGWPAW2011}.  We combine this with the \SVD\ rank-reduction
method of \citet{Cannon:2010p10398} that exploits the redundancy of
the template banks.

>>>>

In this section we describe a decomposition of the \CBC{} signal space that
reduces \TD\ filtering cost sufficiently to allow for the
possibility of \earlywarning\ detection with modest computing requirements.  We
expand on the ideas of \citet{Marion2004} and \citet{Buskulic2010} that describe a
multi-band decomposition of the compact binary signal space that resulted in
a search with minutes latency during S6/VSR3~\citep{HugheyGWPAW2011}.  We combine this
with the \SVD\ rank-reduction method of \citet{Cannon:2010p10398} that exploits
the redundancy of the template banks.
